A Bias-Variance Decomposition of Information Transfer in Multi-Task Learning

### 2020-08-28 arxiv/proof_main.tex
add

	Recall that all tasks have the same covariates in this setting.
	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
	\begin{align}
		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
	\end{align}
	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
	Using the local optimality condition over $B$, that is $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
	\begin{align*}
		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
	\end{align*}
	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obatin
	\begin{align}
		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2. \label{eq_mtl_output_layer}
	\end{align}
	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.
	In order to derive the minimizer, our proof involves two steps.
	First, we consider the expectation of $g(\cW)$ over $\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t$, and $X$.
	We show that the minimizer of $\ex{g(\cW)}$ has a simple closed form solution similar to principal component analysis.
	Second, we show that the concentration error between $g(\cW)$ and $\ex{g(\cW)}$ is small provided with $n$ samples.
	Intuitively, this is because $\cW$ only has $r \times t$ parameters, which is much smaller than $n$ by our assumption.
	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
	\begin{align*}
		Z_0 &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
		Z_1 &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} \\
				&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
		Z_2 &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 \\
				&= \bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i,j\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_j} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_j}.
	\end{align*}
	For the second equation of $Z_1$, we use the fact that $\sum_{j=1}^t X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j W_j^{\top} = X B^{\star} \cW^{\top} = \sum_{j=1}^t X \beta_j W_j^{\top}$.
	For the second equation of $Z_2$, we observe that $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$.
	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as

	\medskip
	\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain the following:
	\begin{align}
		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} - Z_0
		= \exarg{\varepsilon_1, \dots, \varepsilon_t}{Z_2 \mid X}
%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
		= \sigma^2(n\cdot t - p\cdot r) \nonumber
	\end{align}
%	\begin{align}
%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
%	\end{align}
	The first equation uses the same fact the expectation of $Z_1$ over the random noise is zero.
	The second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$.
	We further take expectation over $X$ for $Z_0$ and obtain the following:
	\begin{align*}
		\ex{g(\cW)} = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 (n\cdot t - p \cdot r).
	\end{align*}
	%\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
\iffalse
{\color{red}
\begin{align*}
	f(W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X \hat B W_i - Y_i}^2 = \val(\cal W) \cdot \left( 1+\OO(p^{-1/2+\e})\right),
\end{align*}
where
\begin{align*}
	 \val(\cal W) &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \E_{\e_i:1\le i \le t}\sum_{i=1}^t\left\| X(X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}W_i -\e_i\right\| \\
	 &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \sigma^2 (nt-pr).
\end{align*}

@@

	\medskip
	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
	Next, we show that the concentration errors of $Z_0, Z_1, Z_2$ are all lower order terms compared to $\ex{g(\cW)}$ and scale with $1/\sqrt{p}$.
	For $Z_1$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we conclude that
	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
	where the second part follows by using Cauchy-Shwartz inequality.
	For $Z_0$ and $Z_2$, \todo{add the spectral argument}
	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
	%\begin{align}
	%	g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
	%\end{align}
	%Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.

>>>>

	Recall that all tasks have the same covariates in this setting.
	Therefore, the optimization objective equation \eqref{eq_mtl} becomes the following
	\begin{align}
		f(B; W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X B W_i - Y_i}^2, \label{eq_mtl_same_cov}
	\end{align}
	where $B \in \real^{p \times r}$ and $W_1, W_2, \dots, W_t \in \R^r$ for $1 < r < t$ by our assumption.
	Using the local optimality condition over $B$, that is $\nabla_B f = 0$, we obtain a closed form solution $\hat{B}$ that depends on the output layers as follows
	\begin{align*}
		\hat{B}(W_1, \dots, W_t) &= (X^{\top}X)^{-1} X^{\top} \bigbrace{\sum_{i=1}^t Y_i W_i^{\top}} (\cal W  \cal W^{\top})^{-1} \\
		&= (B^\star \cal W ^{\top}) (\cal W \cal W ^{\top})^{-1} + (X^{\top}X)^{-1}X^{\top}   \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}.
	\end{align*}
	Plugging in the equation $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} we obatin
	\begin{align}
		g(\cal W) = \sum_{j=1}^t \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j + U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - Y_i}^2. \label{eq_mtl_output_layer}
	\end{align}
	Recall that we obtain $\hat{\cW}$ by minimizing $\cW$ in the above equation.
	In order to derive the minimizer, our proof involves two steps.
	First, we consider the expectation of $g(\cW)$ over $\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t$, and $X$.
	We show that the minimizer of $\ex{g(\cW)}$ has a simple closed form solution similar to principal component analysis.
	Second, we show that the concentration error between $g(\cW)$ and $\ex{g(\cW)}$ is small provided with $n$ samples.
	Intuitively, this is because $\cW$ only has $r \times t$ parameters, which is much smaller than $n$ by our assumption.
	Hence we use standard concentration bounds and $\epsilon$-net arguments to show that the concentration error is small for $g(\cW)$.
	To facilitate the analysis, we divide $g(\cW)$ into three parts based on their degree of dependence on the random noise:
	\be\nonumber
	g(\cal W)= g_0 + 2g_1 + g_2, 
	\ee
	where
	\begin{align*}
		g_0(\cal W) &= \sum_{j=1}^t \bignorm{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X\beta_j}^2 = \bignorm{X B^{\star} (\cW^{\top} (\cW\cW^{\top})^{-1} \cW - \id_{t\times t})}^2, \\
		g_1(\cal W)  &= \sum_{j=1}^t \inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j - \varepsilon_j} ,\\
				%&= \sum_{j=1}^t \inner{-X B^{\star} \cW^{\top} (\cW \cW^{\top})^{-1} W_j + X\beta_j}{\varepsilon_j}, \\
		g_2(\cal W)  &= \sum_{j=1}^t \bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j - \varepsilon_j}^2 .
					\end{align*}

	%Now we switch $\hat{B}$ back into equation \eqref{eq_mtl_same_cov} to
	%Then as in \eqref{approxvalid}, we pick $N$ independent samples of the training set for each task with $N\ge n^{1-\e_0}$, and use the concentration result, Lemma \ref{largedeviation}, to get the validation loss as

	\medskip
	\noindent\textbf{The optimal solution of $\ex{g(\cW)}$.}
	We observe that $\ex{g(\cW)}$ admits a bias-variance decomposition as follows.
	First, we take expectation over $\varepsilon_1, \dots, \varepsilon_t$ conditional on $X$ and obtain that
	\begin{align*}
		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= g_0(\cal W) 
		+ \exarg{\varepsilon_1, \dots, \varepsilon_t}{g_2(\cal W)  \mid X} \\
		&=g_0(\cal W) + \exarg{\varepsilon_1, \dots, \varepsilon_t} {\bigbrace{\sum_{j=1}^t \norm{\varepsilon_j}^2} - \sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i} \cdot \bigbrace{\varepsilon_i^{\top} U_X U_X^{\top} \varepsilon_i}}\\
%		=& \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
		&=g_0(\cal W) + \sigma^2(n\cdot t - p\cdot r), \nonumber
	\end{align*}
%	\begin{align}
%		\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X}
%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - X B^{\star}}^2 \nonumber \\
%		&+ \sum_{j=1}^t\bigbrace{\exarg{\varepsilon_1, \dots, \varepsilon_t}{\norm{\varepsilon_j}^2 - 2\inner{U_X U_X^{\top} \sum_{i=1}^t\bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}{\varepsilon_j}} } \nonumber \\
%		&+ \sum_{j=1}^t \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top}
%\bigbrace{\sum_{i=1}^t  \varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j}^2} \nonumber \\
%		=& \norm{XB^{\star} (\cW^{\top}(\cW\cW^{\top})^{-1}\cW - \id)}^2	\label{eq_empirical_1}\\
%			&+ \sum_{j=1}^t \bigbrace{{\ex{\norm{\varepsilon_j}^2}} - \exarg{\varepsilon_1, \dots, \varepsilon_t}{\bignorm{U_X U_X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_t^{\top}} (\cW\cW^{\top})^{-1} W_j}^2 } }  \label{eq_empirical_2}\\
%		=& \bignorm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} \cW - XB^{\star}}^2 + \sigma^2(n\cdot t - p\cdot r) \nonumber
%	\end{align}
	where the first equation uses the fact the expectation of $Z_1$ over the random noise is zero;
	the second equation uses the fact that $\varepsilon_i$ and $\varepsilon_j$ are pairwise independent for any $i \neq j$, and $\sum_{j=1}^t (\cW\cW^{\top})^{-1} W_j W_j^{\top} = \id$; the third equations uses that the variance of every entry of $\varepsilon_i$ is $\sigma^2$ for every $i = 1,\dots, t$, $\tr(U_X U_X^\top)=p$ and $\sum_{1\le i\le t} \bigbrace{W_i^{\top} (\cW \cW^{\top})^{-1} W_i}=\tr(\sum_i W_i W_i^{\top}(\cW \cW^{\top})^{-1})=r$.

	We further take expectation over $X$ for $Z_0$ and obtain the following:
	\begin{align*}
		\ex{g(\cW)} = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 (n\cdot t - p \cdot r).
	\end{align*}
	%\be\label{eq_multival}g(\cal W)=  N\left[\val(\cal W) + t  \sigma^2 \right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right).\ee
\iffalse
{\color{red}
\begin{align*}
	f(W_1, \dots, W_t) = \sum_{i=1}^t \bignorm{X \hat B W_i - Y_i}^2 = \val(\cal W) \cdot \left( 1+\OO(p^{-1/2+\e})\right),
\end{align*}
where
\begin{align*}
	 \val(\cal W) &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \E_{\e_i:1\le i \le t}\sum_{i=1}^t\left\| X(X^{\top}X)^{-1}X^{\top} \bigbrace{\sum_{i=1}^t \varepsilon_i W_i^{\top}} (\cal W \cal W^{\top})^{-1}W_i -\e_i\right\| \\
	 &= \sum_{i=1}^t  \bignorm{X\bigbrace{(B^\star \cal W^\top) (\cal W\cal W^{\top})^{-1} W_i - \beta_i}}^2 + \sigma^2 (nt-pr).
\end{align*}

@@

	\medskip
	\noindent\textbf{The concentration error between $g(\cW)$ and $\ex{g(\cW)}$.}
	Next, we show that the concentration errors of $g_0, g_1, g_2$ are all lower order terms compared to $\ex{g(\cW)}$.
	For $g_1$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we can obtain the following estimates: for $1\le i , j \le t,$
	$$ |\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{\varepsilon_j}| \le p^\e \sigma\|XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j\|,$$
	and
	\begin{align*}  &|\inner{XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1} W_j }| \\
	&\le p^\e \sigma |W_i^{\top} (\cW\cW^{\top})^{-1} W_j|\cdot \|U_X U_X^{\top}( {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j})\|
	\end{align*}
	with high probability for any constant $\e>0$. Inserting the above estimates into $g_1$, we get that
	\begin{align*} 
	 g_1(\cal W)    &\lesssim p^\e \sigma \sum_{j=1}^t \|  {XB^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - X\beta_j}\| \\
	&\le  p^\e \sigma \sum_{j=1}^t \|  \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)\| \cdot \|Z\| \\
	&\lesssim p^{1/2+\e} \sigma \sum_{j=1}^t \|  \Sigma_1^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1}W_j - \beta_j\right)\| \\
	& \le p^{1/2+\e} \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 + \sigma^2 p^{1/2+\e} ,
	\end{align*}
	with high probability for any constant $\e>0$. Here in the second step we used $X=Z\Sigma^{1/2}$, in the third step we used the bound \eqref{eq_isometric} to bound the operator norm $\|Z\|$, and in the last step we used the simple AM-GM inequality.

For $g_2$, using Lemma \ref{largedeviation} in Appendix \ref{sec_maintools} and the fact that all moments of $\varepsilon_i$ exist, we can obtain the following estimates: for $1\le i \ne j \le t,$
\begin{align*}
& |\|\e_j\|^2 - n\sigma^2|=| \langle \e_j ,\e_j\rangle - \E\langle \e_j ,\e_j\rangle | \le \sigma^2 p^{1/2+\e},\\
& |\inner{U_X U_X^{\top} \bigbrace{\varepsilon_i W_i^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}|\le |W_i^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
 &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{\varepsilon_j}\right]\right| \le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j| \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^2\right]\le \sigma^2 p^{1/2+\e},\\
 &\left|\left(1-\mathop{\mathbb{E}}_{\varepsilon_j} \right)\left[\inner{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}{U_X U_X^{\top} \bigbrace{\varepsilon_j W_j^{\top}} (\cW\cW^{\top})^{-1}W_j}\right]\right|\\
 &\le |W_j^{\top} (\cW\cW^{\top})^{-1}W_j|^2 \cdot \sigma^2 p^{\e} \tr \left[(U_X U_X^{\top})^4\right]\le \sigma^2 p^{1/2+\e},
\end{align*}
with high probability for any constant $\e>0$. Inserting the above estimates into $g_1$, we get that
$$\left|g_2(\cal W)-\sigma^2(n\cdot t - p\cdot r)\right|=\left|g_2(\cal W)- \exarg{\varepsilon_1, \dots, \varepsilon_t} {g_2(\cal W)}\right| \lesssim \sigma^2 p^{1/2+\e}$$
with high probability for any constant $\e>0$.

	Finally, for $g_0$ we write it as
	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
	Note that $Zv_j\in \R^n$ is a random vector with i.i.d. entries of mean zero, variance $\|v_j\|^2$, and finite fourth moment by \eqref{assmAhigh}. Hence by law of large numbers, we have 
	$$\frac{\left\|Z v_j \right\|^2 }{ n \|v_j\|^2}=  1+\oo(1) \quad \text{with probability} \ 1-\oo(1), $$
	which implies that 
	$$g_0(\cal W)=n \sum_{j=1}^t \|v_j\|^2 \cdot (1+\oo(1)) = n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1))$$
	with probability $1-\oo(1)$.

	Combining all the above estimates, we obtain that for any constant $\e>0$,
	\begin{align*} 
	g(\cal W)&= n \bignorm{\Sigma^{1/2} B^{\star} (\cW^{\top} (\cW \cW^{\top})^{-1} \cW - \id_{t\times t})}^2 \cdot (1+\oo(1)) + \sigma^2 (n\cdot t - p \cdot r)+\OO(\sigma^2 p^{1/2+\e})\\
	&=\ex{g(\cW)} \cdot (1+\oo(1)) 
	\end{align*}
	with probability $1-\oo(1)$.

%	\[ \abs{Z_1} \le \sum_{j=1}^t \sigma \cdot \norm{X B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j - X \beta_j} \le \sigma \cdot \sqrt{t \cdot Z_0}, \]
%	where the second part follows by using Cauchy-Shwartz inequality.

	%We provide tights bounds on the concentration error from the randomness of $\varepsilon_1, \dots, \varepsilon_t$, and $X$, respectively.
	%\begin{align}
	%	g(\cW) &= \exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} \cdot (1 \pm \OO(p^{-1/2 + c})), \text{ and} \label{approxvalid_1} \\
	%	\exarg{\varepsilon_1, \dots, \varepsilon_t}{g(\cW) \mid X} &= \ex{g(\cW)} \cdot(1 + o(1)) \label{approxvalid_2}
	%\end{align}
	%Together, they imply that $g(\cW) = \ex{g(\cW)} \cdot (1 + o(1))$. Therefore, next we focus on proving equation \eqref{approxvalid_1} and \eqref{approxvalid_2}.
